---
title: "project"
author: "Jenniferpsy"
date: "2017年6月27日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load data
```{r cars}
unzip("C://Users//lenovo//Desktop//repdata_data_activity.zip",exdir="C://Users//lenovo//Desktop")
data <- read.csv("C://Users//lenovo//Desktop//activity.csv")
head(data)
```

## The mean and median of the total number of steps taken per day

```{r pressure, echo=FALSE}
sumstat<-tapply(data[,1],as.factor(data[,2]),sum)
hist(sumstat,20,main="the total number of steps taken each day",xlab="total/day",ylab="frequency")
meanstat<-mean(sumstat,na.rm=T);meanstat
medianstat<-median(sumstat,na.rm=T);medianstat
```

So the mean of the total number of steps taken per day is 10766.19;  the median is 10765.

## Average daily activity pattern
```{r q3, echo=FALSE}
m<-aggregate(steps~interval,data,mean,na.rm=T)
plot(m[,1],m[,2],type="l",xlab="interval",ylab="the mean of steps")
m[which(m[,2]==max(m[,2])),]
```
So on average across all the days, the 835th interval contains the maximum number of steps.

##Imputing missing values
####the total number of rows with NAs
```{r q4, echo=FALSE}
good<-complete.cases(data)
gooddata<-data[good,]
dim(gooddata)
```
So the total number of rows with NAs is 15264.

####filling in all of the missing values
There I will fill the NAs by using the mean for that 5-minute interval.
```{r q5, echo=FALSE}
newsteps=c()
attach(data)
for(i in 1:length(steps)){
  if(is.na(steps[i])==T){
    q=data[i,3]
    newsteps[i]=m[which(interval==q),2][1]
  }else{
    newsteps[i]=steps[i]
  }
}
newdata<-data[,-1]
newdata$newsteps<-newsteps
head(newdata)
```
#### The mean and median of the total number of steps taken per day for newdata
```{r q6, echo=FALSE}
newsumstat<-tapply(newdata[,3],as.factor(newdata[,1]),sum)
hist(newsumstat,20,main="the total number of steps taken each day",xlab="total/day",ylab="frequency")
newmeanstat<-mean(newsumstat,na.rm=T);newmeanstat
newmedianstat<-median(newsumstat,na.rm=T);newmedianstat
```

So the mean of the total number of steps taken per day is 10766.19;  the median is 10766.19. 
In conclusion, the mean does not change, but the median gets larger.

## Explore difference between weekday and weekend
```{r q7, echo=FALSE}
attach(newdata)
newdate=as.Date(newdata$date)
a=weekdays(newdate)
newdata$a<-a
b=c()
for(i in 1:dim(newdata)[1]){
  if(newdata[i,4]=="星期六"|newdata[i,4]=="星期日"){
    b[i]="weekend"
  }
  else{
    b[i]="weekday"
  }
}
newdata$indicator<-as.factor(b)
head(newdata)

```

####A panel plot
```{r q8, echo=FALSE}

newdata$indicator<-as.factor(b)
attach(newdata)
mm<-aggregate(newsteps,by=list(indicator,interval),mean)
library(lattice)
xyplot(mm[,3]~ mm[,2]| mm[,1], data = mm, layout = c(1, 2),xlab="interval",ylab="the mean of steps",type="l")

```